---
title: "ClassWork"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


## Class 2/25/2019 - Data Visualization

-dataframe format - put the data in this format to analyse (like excel)
-use ggplot2 to graph

a <- data.frame()


Names <- c("Peter, Paul, Mary")
Age <- c(1000,1200,100)
Sex <- c("M", "M", "F")

my_df(name of the dataframe)  data.frame(Names,Ages, Sex)
my_df <- data.frame (Names, Age, Sex)
creates a table with 3 collumns (names, ages, sex)

Put NA for missing data or for nothing (50-NA(missing name and sex))

creates a table with 3 collumns (names, ages, sex)

my_df and $ gives a particular column, AND GIVES LEVELS !!!
my_df$names and it will show data for names and it's levels

my_df$names <- as.character(my_df$names) will transform the data from factor to character in global environment


```{r}

Names <- c("Peter", "Paul", "Mary", "NA")
Age <- c(1000,1200,100, 50)
Sex <- c("M", "M", "F", "NA")

my_df <- data.frame (Names, Age, Sex)
```

Example 1.

1)instal ggplot 2 from packages
aes(x=a,y=b) - defines the axes and veriables x axes is a variable, y axes is b variable
ggplot(plot_df) to run ggplot on a datafram

geoms - for graphs. geom_point
```{r}

library(ggplot2)
a <- c(1,2,3,2,3,4,5,4)
b <- c(4,3,4,3,2,1,2,3)
plot_df <- data.frame(a,b)


ggplot(plot_df, aes(x=a,y=b))

ggplot(plot_df, aes(x=a,y=b))+
  geom_point()


```


ggplot(plot_df, aes(x=a,y=b))+
  geom_point(size=2)+  ----SIZE of the dots
  geom_smooth(method=lm)+  --------lenear regression
  coord_cartesian(xlim=c(0,7),ylim=c(0,10))+  -------- changesthe range x and y limits
  xlab("x-axis label")+ ------------ change the names of x axis
  ylab("y-axis label")+ ----------- change the name of y axis
  ggtitle("I made a scatterplot")+  
  theme_classic(base_size=12)+   ----------classic background, base_size ----- size of font on the graph
  theme(plot.title = element_text(hjust = 0.5)) ------------- centers the title
  
  
```{r}
ggplot(plot_df, aes(x=a,y=b))+
  geom_point(size=2)+
  geom_smooth(method=lm)+
  coord_cartesian(xlim=c(0,7),ylim=c(0,10))+
  xlab("x-axis label")+
  ylab("y-axis label")+
  ggtitle("I made a scatterplot")+
  theme_classic(base_size=12)+
  theme(plot.title = element_text(hjust = 0.5))
```

factor_one <- as.factor(c("A","B","C"))
dv_means <- c(20,30,40)
dv_SEs   <- c(4,3.4,4)
plot_df <- data.frame(factor_one, -------------levels of the factors
                      dv_means,
                      dv_SEs)
                      dv_SEs)
# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means))+
  geom_bar(stat="identity")                     
  
  add + to add stuff to the graph.
  geom_bar (stat="identity")  ----------- plot the data on the graph, without it, it won't work
  
# adding error bars, customizing

ggplot(plot_df, aes(x=factor_one,y=dv_means))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=dv_means-dv_SEs, ------------need to identify minimum value, mean -stnderror
                    ymax=dv_means+dv_SEs), ------------ need to identify maximum value,mean+stnderror
                width=.2)+
  coord_cartesian(ylim=c(0,100))+
  xlab("x-axis label")+
  ylab("y-axis label")+
  ggtitle("I made a bar graph")+
  theme_classic(base_size=12)+
  theme(plot.title = element_text(hjust = 0.5))

```{r}
factor_one <- as.factor(c("A","B","C"))
dv_means <- c(20,30,40)
dv_SEs   <- c(4,3.4,4)
plot_df <- data.frame(factor_one,
                      dv_means,
                      dv_SEs)
# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means))+
  geom_bar(stat="identity")

```


#Create a dataframe
factor_one <- rep(as.factor(c("A","B","C")),2)
factor_two <- rep(as.factor(c("IIA","IIB")),3)
dv_means <- c(20,30,40,20,40,40)
dv_SEs   <- c(4,3.4,4,3,2,4)
plot_df <- data.frame(factor_one,
                      factor_two,
                      dv_means,
                      dv_SEs)

# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means,
                    group=factor_two,
                    color=factor_two
                    fill_factor_two))+---------------------means border color. fill=factor_two to color the bar
  geom_bar(stat="identity", position="dodge")-------------- dodge separates the bars of different factors
  
```{r}
#Create a dataframe
factor_one <- rep(as.factor(c("A","B","C")),2)
factor_two <- rep(as.factor(c("IIA","IIB")),3)
dv_means <- c(20,30,40,20,40,40)
dv_SEs   <- c(4,3.4,4,3,2,4)
plot_df <- data.frame(factor_one,
                      factor_two,
                      dv_means,
                      dv_SEs)

# basic bar graph

ggplot(plot_df, aes(x=factor_one,y=dv_means,
                    group=factor_two,
                    color=factor_two))+
  geom_bar(stat="identity", position="dodge")
```

```{r}
factor_one
```

geom_errorbar(aes(ymin=dv_means-dv_SEs,
                    ymax=dv_means+dv_SEs),
                position=position_dodge(width=0.9)  ------------------ positions the error bars in the center of the bar.
                
                
facet_wrap(~factor_three) ----------- divides the data on a graphs, in this example 2 graphs for 3 factors