---
title: "R Basics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
### Simple Math

5+6

23-64

25*5

266/6

```{r}
5+6
23-64
25*5
266/6
```

### Numbers into variables


```{r}
a <- 522
b <- 2333
a+b 
```
### Numbers 1 to 100 into variable


```{r}
x <- (1:100) 

x

```


### Sum of all numbers 1 to 100

```{r}
sum(1:100)
```

### Write a function to find the sum of all integers between any two values.

```{r}
MyFirstFunction <-function(y) {
  TotalSum <-0
  for (i in y){
    TotalSum<-TotalSum+i
  }
  return(TotalSum)
}

numbers<-c(1:100)
MyFirstFunction(numbers)

```
### all of the odd numbers from 1 to 100

```{r}
seq(1:100 )
```

#  Data Visualization

```{r}
library(ggplot2)

```
Error: package or namespace load failed for ‘ggpubr’ in loadNamespace(j <- i[[1L]], c(lib.loc, .libPaths()), versionCheck = vI[[j]]): there is no package called ‘tidyselect’

```{r}

Nonsocial<-c(0,1,2,4,26,46,53,59)
Social<-c(12,46,4,41,48,33,56,58)
plot_df<-data.frame(Nonsocial,Social)

ggplot(plot_df, aes(x=Nonsocial,y=Social))+
  geom_point()+
  geom_smooth(method=lm,se=FALSE,fill="black")+
  xlab("Average Frequency of Nonsocial Risk")+
  ylab("Average Frequency of Social Risk")+
  coord_cartesian(xlim=c(0,70),ylim=c(0,70))+
  scale_x_continuous(breaks=seq(0,70,10), expand=c(0,0))+
  scale_y_continuous(breaks=seq(0,70,10), expand=c(0,0))+
  theme_classic()

```


```{r}
Condition <-rep(c("NoTransient","Transient"), each=2)
CG <-rep(c("Outside","Inside"),2)
RT <- rep(c(301,303,280,291))
plot_df <- data.frame(Condition, RT, CG)


ggplot(plot_df, aes(x=Condition,y=RT,group=CG,fill=CG))+
  geom_bar(stat="identity",position="dodge",color="black",size=.25)+
  coord_cartesian(ylim=c(230,340))+
  scale_y_continuous(breaks=seq(230,340,10))+
  ylab("Mean Median RT (ms)")+
  scale_fill_brewer(palette="Greys", direction=-1)+
  theme_classic()+
ggtitle("Visual Group")

Condition <-rep(c("NoTransient","Transient"), each=2)
CG <-rep(c("Outside","Inside"),2)
RT <- rep(c(290,295,250,265))
plot_df <- data.frame(Condition, RT, CG)


 ggplot(plot_df, aes(x=Condition,y=RT,group=CG,fill=CG))+
  geom_bar(stat="identity",position="dodge", 
           color="black",
           size=.25)+
  coord_cartesian(ylim=c(230,340))+
  scale_y_continuous(breaks=seq(230,340,10))+
  ylab("Mean Median RT (ms)")+
  scale_fill_brewer(palette="Greys", direction=-1)+
  theme_classic()+
ggtitle("Auditory Group")
```

```{r}
Surgeon <-rep(c("Men Performed Surgery \n n = 152",
            "Women Performed Surgery \n n = 142"), each =3)
Condition <-rep(c("Prior", "Model \n Posterior","Reported \n Posterior"), 2)
Percentege <- c(.7, .88, .87, .29, .72, .74)
plot_df <- data.frame(Surgeon, Condition, Percentege)

ggplot(plot_df, aes(x=Condition, y=Percentege, fill=Condition))+
  geom_bar(stat="identity", position="dodge")+
  ylab("P(Target = Doctor)")+
  coord_cartesian(ylim=c(0,1))+
  scale_y_continuous(breaks=seq(0,1,.1),labels = scales::percent)+
  facet_wrap(~Surgeon)+
  theme_classic()
```


```{r}
Social <- c(-2.4 , -2.4, -2.4 , 0, 0, 0, 2.4, 2.5, 2.7)
AS <- c(-6,-1,11, -1,-1,-2,-8,-6,4)
plot_df <- data.frame(Social,AS)

ggplot(plot_df, aes(x=Social,y=AS))+
  geom_point()+
  geom_smooth(method=lm,se=FALSE,fill="black")+
  xlab("Social N400")+
  ylab("Autism-Spectrum \n Quotient (score)")+
  scale_x_continuous(breaks=seq(-2.5,2.5,2.5))+
  coord_cartesian(xlim=c(-2.5,5))

Social <- c(-2.5, -2.4, -2.3, 0, 0, 2.4, 2.5)
RM <- c(-1, 2, 3, -3, -2, 5, -3)
plot_df <- data.frame(Social,RM)

ggplot(plot_df, aes(x=Social,y=RM))+
  geom_point()+
  geom_smooth(method=lm,se=FALSE,fill="black")+
  xlab("Social N400")+
  ylab("Reading the Mind in the \n Eyes Test (score)")+
  scale_x_continuous(breaks=seq(-2.5,2.5,2.5))+
  coord_cartesian(xlim=c(-2.5,5))

Social <- c(-2.4, -2.4,-2.4, 0,0,0,2.4,2.5)
EQT <- c(-13,11,29,8,8,8, 12, 5)
plot_df <- data.frame(Social,EQT)

ggplot(plot_df, aes(x=Social,y=EQT))+
  geom_point()+
  geom_smooth(method=lm,se=FALSE,fill="black")+
  xlab("Social N400")+
  ylab("Empathy Quotient Test \n  (score)")+
  scale_x_continuous(breaks=seq(-2.5,2.5,2.5))+
  coord_cartesian(xlim=c(-2.5,5))
```



#  Statistics Assignment

```{r}

hist(rnorm(n=100000,mean=0,sd=1))
mean(rnorm(n=100000, mean=0, sd=10))
sd(rnorm(n=100000, mean=0, sd=10))


#1sample mean,when n=10

means<-c()
for(i in 1:10000){
means[1]<-mean(rnorm(n=10, mean=0, sd=10))
}

means



#replicate-how many time we want to repeat function. 
#SEM = standart error of the mean, 



replicate(10000, mean(rnorm(n=10, mean=0, sd=1)))

A <- rnorm(10,0,1)
B <- rnorm(10,0,1)
MD <- mean(A)-mean(B)

MD

mean_differences <- replicate(1000, mean (rnorm(10,0,1))-mean(rnorm(10,0,1)))

sort(mean_differences)[250]
sort(mean_differences)[750]


hist(mean_differences)


```




#pt function getting p-value- of  t value. t is a q. q is a t for pt and pq functions.

```{r}

pt(q=2,df=9)

pt(q=c(0.5,1,1.5,2,2.5),df=9)

```

```{r}
pt(q=c(0.5,1,1.5,2,2.5),df=9)

t.test(rnorm(10,0,1),mu=0)

t.test(rnorm(10,0,1),mu=0)$statistic

t_s <- replicate(10000,t.test(rnorm(10,0,1),mu=0)$statistic)

hist(t_s)

length(t_s[t_s < 0.5])/10000
length(t_s[t_s < 1])/10000
length(t_s[t_s < 1.5])/10000
length(t_s[t_s < 2])/10000
length(t_s[t_s < 2.5])/10000
```


#correlation. from 10-to-100

```{r}

cor(rnorm(10,0,1),rnorm(10,0,1))

replicate(10000, cor(rnorm(10,0,1),rnorm(10,0,1)))

hist(replicate(10000, cor(rnorm(100,0,1),rnorm(100,0,1))))

simrs <-replicate(10000, cor(rnorm(100,0,1),rnorm(100,0,1)))

sort(abs(simrs))[9500]

```


#F simulation

```{r}
library(ggplot2)
A<- c(1,2,3,4)
B<- c(3,4,5,6)
C<- c(5,6,7,8)

conds<-rep(c("A", "B", "C"),each=4)
DV <- c(A,B,C)
df <-data.frame(conds,DV)
summary(aov(DV~conds,df))

```

```{r}
run_anova <-function(){
A<-rnorm(4,0,1)
B<-rnorm(4,0,1)
C<-rnorm(4,0,1)

conds<- rep(c("A","B","C"), each=4)
DV <- c(A,B,C)
df <- data.frame(conds, DV)
sum_out <-summary(aov(DV~conds,df))
return (sum_out[[1]]$'F value'[1])
}

save_fs <-replicate(10000, run_anova())
hist(save_fs)
sort(save_fs)[9500]

```


RT 14.47, 19.99, 14.10, 19.22, 16.68, 9.88, 12.40, 9.40, 20.93, 7.90, 14.95, 13.19, 16.59, 16.59, 10.57, 10.42, 14.26, 11.63

Funinness 5.41, 7.09, 9.82, 3.68, 6.59, 7.64, 6.77, 5.45, 6.82, 7.41, 9.59, 7.05, 6.50, 7.18, 5.68, 7.09, 6.18, 4.91

HUMOR PRODUCTION SCORE 40.65, 42.85, 41.22, 37.79, 40.89, 40.71, 45.15, 39.83, 40.77, 43.78, 41.40, 43.61, 44.25, 44.26, 43.94, 45.24, 44.60, 43.33, 
HUMOR COMPREHENSION SCORE
60.2, 66.0, 60.2, 51.2, 55.5, 55.5, 82.2, 49.1, 53.3, 60.2, 66.0, 60.2, 62.9, 62.9, 66.0, 57.8, 57.8, 60.2

RAW HUMOR COMPREHENSION SCORE 16, 18, 16, 12, 14, 14, 21, 11, 13, 16, 18, 16, 17, 17, 18, 15, 15, 16, 

comprehansion and production

```{r}

Production <-c(40.65, 42.85, 41.22, 37.79, 40.89, 40.71, 45.15, 39.83, 40.77, 43.78, 41.40, 43.61, 44.25, 44.26, 43.94, 45.24, 44.60, 43.33)

Comprehansion <-c(60.2, 66.0, 60.2, 51.2, 55.5, 55.5, 82.2, 49.1, 53.3, 60.2, 66.0, 60.2, 62.9, 62.9, 66.0, 57.8, 57.8, 60.2)

cor.test(Production, Comprehansion)

```

hypothesis 1
```{r}

RT <-c(14.47, 19.99, 14.10, 19.22, 16.68, 9.88, 12.40, 9.40, 20.93, 7.90, 14.95, 13.19, 16.59, 16.59, 10.57, 10.42, 14.26, 11.63)

Funinness <-c(5.41, 7.09, 9.82, 3.68, 6.59, 7.64, 6.77, 5.45, 6.82, 7.41, 9.59, 7.05, 6.50, 7.18, 5.68, 7.09, 6.18, 4.91)

cor.test(RT,Funinness)

```



```{r}
Raw <- c(16, 18, 16, 12, 14, 14, 21, 11, 13, 16, 18, 16, 17, 17, 18, 15, 15, 16)
Funinness <- c(5.41, 7.09, 9.82, 3.68, 6.59, 7.64, 6.77, 5.45, 6.82, 7.41, 9.59, 7.05, 6.50, 7.18, 5.68, 7.09, 6.18, 4.91)

cor.test(Raw,Funinness)
```

```{r}
Production <-c(40.65, 42.85, 41.22, 37.79, 40.89, 40.71, 45.15, 39.83, 40.77, 43.78, 41.40, 43.61, 44.25, 44.26, 43.94, 45.24, 44.60, 43.33)

Funinness <-c(5.41, 7.09, 9.82, 3.68, 6.59, 7.64, 6.77, 5.45, 6.82, 7.41, 9.59, 7.05, 6.50, 7.18, 5.68, 7.09, 6.18, 4.91)

cor.test(Production, Funinness)

plot(Production, Funinness)

```



```{r}
plot(Production, Comprehansion, xlab='Humor production score', ylab='Humor comprehansion', main='Scatterplot of response time and Funiness rating', pch=20)


```


```{r}

plot(RT, Funinness,xlab='Response time', ylab='Funiness rating', main='Scatterplot of response time and funinness rating', pch=20)

```


```{r}
plot(Raw, Funinness,xlab='Raw scores', ylab='Funiness rating', main='Scatterplot of raw scores and funinness rating', pch=20)
```

```{r}
plot(Production, Funinness,xlab='HUmor production scores', ylab='Funiness rating', main='Scatterplot of humor production scores and funinness rating', pch=20)
```

