---
title: "R Basics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
### Simple Math

5+6

23-64

25*5

266/6

```{r}
5+6
23-64
25*5
266/6
```

### Numbers into variables


```{r}
a <- 522
b <- 2333
a+b 
```
### Numbers 1 to 100 into variable


```{r}
x <- (1:100) 

x

```


### Sum of all numbers 1 to 100

```{r}
sum(1:100)
```

### Write a function to find the sum of all integers between any two values.

```{r}
MyFirstFunction <-function(y) {
  TotalSum <-0
  for (i in y){
    TotalSum<-TotalSum+i
  }
  return(TotalSum)
}

numbers<-c(1:100)
MyFirstFunction(numbers)

```
### all of the odd numbers from 1 to 100

```{r}
seq(1:100 )
```

# Class 2/25/2019 - Data Visualization

columns:
  names, MF(mean frequency), Condition
  Dara      60                  SC
  Dara      60                  NS
  Rita      55                  SC
  Rita      55                  NS
  Aversity <- rep(c("A", "N_A")), times=c(4,6) ------------ repeats labels different amount of times a 4 times and n_a 6 times. 
  
  how to make random numbers????rnorm command??????????
  rep command?????????????
  c??????????????
  
```{r}
Names <- rep(c("Dara", "Azelea", "Barbi", "Rowena", "Fiona"),each=2)
MF <-rnorm (10,45,25)
Condition <- c("Social", "NonSocial")
Aversity <- rep(c("A", "N_A"),times=c(4,6))
                
plot_df<- data.frame (Names, MF, Condition, Aversity)

ggplot(plot_df, aes(x=Condition, y=MF, group=Names,linetype=Aversity))+
  geom_line()+
  geom_text(label=Names)+
  theme_classic()

```

```{r}

```

